Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-16 Manuscript/proof_outline.tex
rewrite explanation of addContent and extendContent

\noindent
For additive contents, we need two
definitions. \leanlinecolor{AddContent} defines a set-function
\leanline{toFun} on \leanline{Set α}, whereas
\leanlinecolor{extendContent} comes with \leanline{m : ∀ s : Set α, s ∈ C → ℝ≥0∞}.

>>>>

\noindent
For additive contents, we need two definitions.
The structure \leanlinecolor{AddContent} defines
an additive set-function \leanline{toFun} on \leanline{Set α}.
The definition \leanlinecolor{extendContent} takes an additive function defined only on a semi-ring of sets, and extends it to an additive content on all sets by choosing the value infinity outside of the semi-ring. We use this because total functions are easier to use in subsequent code.
